---
title: "Descriptive statistics"
---

```{r Global, echo=FALSE, message=FALSE, warning=FALSE}
source("Global.R")
```

# {.tabset .tabset-pills}
## Pathologic features {.tabset .tabset-pills}
### Histologic subtype
```{r subtype}
x <- fct_infreq(DB$subtype)
tbl_nice(x)
g_nice(x)
```

### Histologic grade
```{r grade}
x <- DB$grade
tbl_nice(x)
g_nice(x)
```

## PD-L1 {.tabset .tabset-pills}
### Tumor PD-L1+, %
```{r pdl1_tumor}
x <- DB$pdl1_tumor
tbl_nice(x)
g_nice(x)

DF <- DB %>% 
  mutate(
    pdl1_tumor_positivity = factor(
      ifelse(
        pdl1_tumor == 0,
        "No PD-L1 positivity",
        "Any PD-L1 positivity"
      )
    )
  )

x <- DF$pdl1_tumor_positivity
tbl_nice(x)
g_nice(x)

```

### Tumor PD-L1+, H-score
```{r pdl1_tumor_h}
x <- DB$pdl1_tumor_h
tbl_nice(x)
g_nice(x)
```

### Tumor PD-L1+, location
```{r pdl1_tumor_location}
x <- DB$pdl1_tumor_location
tbl_nice(x)
g_nice(x)
```

### Stromal PD-L1+, %
```{r pdl1_lymph}
x <- DB$pdl1_lymph
tbl_nice(x)
g_nice(x)

DF <- DB %>% 
  mutate(
    pdl1_lymph_positivity = factor(
      ifelse(
        pdl1_lymph == 0,
        "No PD-L1 positivity",
        "Any PD-L1 positivity"
      )
    )
  )

x <- DF$pdl1_lymph_positivity
tbl_nice(x)
g_nice(x)
```

### Host response
```{r host_response}
x <- DB$host_response
tbl_nice(x)
g_nice(x)
```

## FOXP3 {.tabset .tabset-pills}
### Intratumor FOXP3+ lymphocytes, N
```{r foxp3_lymph_tumor}
x <- DB$foxp3_lymph_tumor
tbl_nice(x)
g_nice(x)
```

### Stromal FOXP3+ lymphocytes, N
```{r foxp3_lymph_stroma}
x <- DB$foxp3_lymph_stroma
tbl_nice(x)
g_nice(x)
```

### Tumor FOXP3+
```{r foxp3_tumor}
x <- DB$foxp3_tumor
tbl_nice(x)
g_nice(x)
```

## CD8/Ki-67 {.tabset .tabset-pills}
### Intratumoral CD8+ lymphocytes, N
```{r cd8_tumor}
x <- DB$cd8_tumor
tbl_nice(x)
g_nice(x)
```

### Intratumoral CD8+/Ki-67+ lymphocytes, N
```{r cd8ki67_tumor}
x <- DB$cd8ki67_tumor
tbl_nice(x)
g_nice(x)
```

### Stromal CD8+ lymphocytes, N
```{r cd8_stroma}
x <- DB$cd8_stroma
tbl_nice(x)
g_nice(x)
```

### Stromal CD8+/Ki-67+ lymphocytes, N
```{r cd8ki67_stroma}
x <- DB$cd8ki67_stroma
tbl_nice(x)
g_nice(x)
```

### Ki-67+ tumor cells, N
```{r ki67_tumor}
x <- DB$ki67_tumor
tbl_nice(x)
g_nice(x)
```
